Exact asymptotic expressions for local clustering in hyperbolic random graphs

### 2018-10-24 introduction.tex
fix typos in main results section 1.5

With these expressions we define the limit local clustering coefficient as
\begin{equation}\label{eq:def_average_clustering_infinite_model}
	c_\infty := \alpha \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) e^{-\alpha y} \dd y,
\end{equation}
while the local clustering function limit is defined as
\begin{equation}\label{eq:def_c_infty_k}
	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) e^{-\alpha y} \dd y}.
\end{equation}

@@

Our first result shows that the local clustering coefficient in the Hyperbolic random graph converges in expectation to $c_\infty$.

@@

Next we establishes the full expression for the clustering coefficient $c_\infty$ in terms of the special function defined above.

\begin{theorem}[Exact expression for clustering coefficient limit]\label{thm:exact_expression_c_infty}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, if $\alpha \ne 1$
\begin{align*}
	c_\infty 
	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
		{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
		+  \frac{2^{-1 - 4 \alpha}}{(\alpha - 1)^2} \\
	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}
		{2 (\alpha - 1) (3 \alpha - 1)} \\
	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{2\alpha} \Gamma^\ast( - 2 \alpha, \xi_{\alpha,\nu})}{4(\alpha-1)}
		+ \frac{\xi_{\alpha,\nu}^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \Gamma^\ast(- 2 \alpha - 2, \xi_{\alpha,\nu})}
		{2(\alpha-1)^2} \\
	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{2\alpha + 1}\alpha (2\alpha - 1) \Gamma^\ast( - 2 \alpha - 1,\xi_{\alpha,\nu})}{(\alpha-1)}
		- \frac{\xi_{\alpha,\nu}^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)^2}\\
	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)} \\
	&\hspace{10pt}- \frac{e^{-\xi_{\alpha,\nu}} \Gamma(2\alpha+1) 
		\left(U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) + U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu})\right)}{4(\alpha-1)} \\
	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{6\alpha - 2} \Gamma(2\alpha+1)\left( 	
		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}
		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}\right)}{4(\alpha-1)},
\end{align*}
while for $\alpha = 1$,
\begin{align*}
	c_\infty &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
\end{align*}
with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function\footnote{Note that the integrals in the expression for $c_\infty$ for $\alpha = 1$ exists: for the first one note that $1-4z+3z^2=(1-z)(1-3z)$, so the integrand can be bounded by $C(1-z)\log(1-z)$ on $[0,1)$ for some constant $C$, which can be continued continuously to the compact interval $[0,1]$ by noting that the limit for $z \rightarrow 1$ is zero, so the integrand is bounded on a bounded domain and hence, this integral is finite; for the second integral note that $\Li_2(z)$ is bounded by $\Li_2(1)$ on $[0,1]$, which is a series with well-known finite limit, so again the integrand is bounded on a bounded domain and hence the second integral is also finite.}. 
\end{theorem}

@@

\begin{theorem}[Exact expression for local clustering function limit]
\label{thm:exact_expression_local_clustering}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, for $\alpha \ne 1$
\begin{align*}
	c_\infty(k) 
	&= \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma^+(k-6\alpha + 2,\xi_{\alpha,\nu})}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
		\left(\frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha - 1)^2} + \frac{(\alpha - \frac{1}{2})B^-\left(\frac{1}{2},2\alpha + 1, 2\alpha - 2\right)}{2\alpha(\alpha - 1)}\right)\\
	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma(2\alpha + 1)}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}\\
	&\hspace{10pt}+ \frac{1}{8\alpha(\alpha - 1)}
		\left(\frac{\xi_{\alpha,\nu}^{k-2\alpha}e^{-\xi}U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})}
		{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}-1\right)\\
	&\hspace{10pt}- \frac{(\alpha - 1/2)^2 \xi_{\alpha,\nu}^2 \Gamma^+(k-2\alpha -2,\xi_{\alpha,\nu})}
		{4(\alpha - 1)^2 \Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
\end{align*}
while for $\alpha = 1$
\begin{align*}
	c_\infty(k) &= \frac{9 \eta^3}{2 k!} 	
		\Gamma^+(k-3,\eta)-\frac{\xi_{\alpha,\nu}^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
\end{align*}
with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
\end{theorem}

From the exact expression for $c_\infty(k)$ we obtain its asymptotic behavior as $k \to \infty$. For this we first define, for any $\frac{1}{2} < \alpha < \frac{3}{4}$,
\begin{equation}\label{eq:def_C_alpha}
	C_\alpha = \frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha-1)^2} 
	+ \frac{\alpha - \frac{1}{2}}{2(\alpha - 1)\alpha} B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)
	- \frac{1}{4(\alpha - 1)}B(2\alpha, 3\alpha - 4).
\end{equation}
Moreover, to simplify the statement we define the scaling function 
\begin{equation}\label{eq:def_scaling_function}
s_\alpha(k_n) = \begin{cases} 
		k^{4\alpha-1} &\frac{1}{2}<\alpha<\frac{3}{4}, \\
		\frac{k}{\log(k)} & \alpha = \frac{3}{4}, \\
		k &\alpha > \frac{3}{4}.
\end{cases}
\end{equation}

>>>>

With these expressions we define the limiting local clustering coefficient as
\begin{equation}\label{eq:def_average_clustering_infinite_model}
	c_\infty := \alpha \int_0^\infty \Delta_{\Pcal}(y) (1 - \rho(y,0) - \rho(y,1)) e^{-\alpha y} \dd y,
\end{equation}
while the limiting local clustering function is defined as
\begin{equation}\label{eq:def_c_infty_k}
	c_\infty(k) = \frac{\int_0^\infty \rho(y,k) \Delta_\Pcal(y) e^{-\alpha y} \dd y}{\int_0^\infty \rho(y,k) e^{-\alpha y} \dd y}.
\end{equation}

@@

Our first result shows that the local clustering coefficient of the hyperbolic random graph converges in expectation to $c_\infty$.

@@

Next we establish the full expression for the limiting clustering coefficient $c_\infty$ in terms of the special functions defined above.

\begin{theorem}[Exact expression for limiting clustering coefficient]\label{thm:exact_expression_c_infty}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, if $\alpha \ne 1$
\begin{align*}
	c_\infty 
	&=\frac{2 + 4 \alpha + 13 \alpha^2 - 34 \alpha^3 - 12\alpha^4 + 24 \alpha^5}
		{16(\alpha-1)^2 \alpha (\alpha+1) (2\alpha+1)} 
		+  \frac{2^{-1 - 4 \alpha}}{(\alpha - 1)^2} \\
	&\hspace{10pt}+ \frac{(\alpha - 1/2) (B(2 \alpha, 2 \alpha + 1) + B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha))}
		{2 (\alpha - 1) (3 \alpha - 1)} \\
	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{2\alpha} \Gamma^\ast( - 2 \alpha, \xi_{\alpha,\nu})}{4(\alpha-1)}
		+ \frac{\xi_{\alpha,\nu}^{2\alpha + 2}\alpha (\alpha - 1/2)^2 \Gamma^\ast(- 2 \alpha - 2, \xi_{\alpha,\nu})}
		{2(\alpha-1)^2} \\
	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{2\alpha + 1}\alpha (2\alpha - 1) \Gamma^\ast( - 2 \alpha - 1,\xi_{\alpha,\nu})}{(\alpha-1)}
		- \frac{\xi_{\alpha,\nu}^{6\alpha-2}2^{-4\alpha}(3\alpha - 1)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)^2}\\
	&\hspace{10pt}-\frac{\xi_{\alpha,\nu}^{6\alpha - 2}(\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha)\Gamma^\ast( - 6 \alpha + 2, \xi_{\alpha,\nu})}{(\alpha-1)} \\
	&\hspace{10pt}- \frac{e^{-\xi_{\alpha,\nu}} \Gamma(2\alpha+1) 
		\left(U(2\alpha+1,1-2\alpha,\xi_{\alpha,\nu}) + U(2\alpha+1,2-2\alpha,\xi_{\alpha,\nu})\right)}{4(\alpha-1)} \\
	&\hspace{10pt}+ \frac{\xi_{\alpha,\nu}^{6\alpha - 2} \Gamma(2\alpha+1)\left( 	
		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+2,0}{\xi_{\alpha,\nu}}
		+ \MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+3,0}{\xi_{\alpha,\nu}}\right)}{4(\alpha-1)},
\end{align*}
while for $\alpha = 1$,
\begin{align*}
	c_\infty &= \frac{575 - 12 \pi^2}{576} + \frac{\eta^4(7 + \pi^2)\Gamma^\ast(-4, \eta)}{4}\\
	&\hspace{10pt}- \frac{1}{2} \int_0^1 (1 - 4z + 3z^3)\log(1-z)(z + \eta)e^{-\eta/z} \dd z\\
	&\hspace{10pt}- \int_0^1 \Li_2(z)(z^3 + \eta z^2) e^{-\eta/z} \dd z,		
\end{align*}
with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function\footnote{Note that the integrals in the expression for $c_\infty$ for $\alpha = 1$ exists: for the first one note that $1-4z+3z^2=(1-z)(1-3z)$, so the integrand can be bounded by $C(1-z)\log(1-z)$ on $[0,1)$ for some constant $C$, which can be continued continuously to the compact interval $[0,1]$ by noting that the limit for $z \rightarrow 1$ is zero, so the integrand is bounded on a bounded domain and hence, this integral is finite; for the second integral note that $\Li_2(z)$ is bounded by $\Li_2(1)$ on $[0,1]$, which is a series with well-known finite limit, so again the integrand is bounded on a bounded domain and hence the second integral is also finite.}. 
\end{theorem}

@@

\begin{theorem}[Exact expression for limiting local clustering function]
\label{thm:exact_expression_local_clustering}
Let $\alpha > \frac{1}{2}$, $\nu > 0$. Then, for $\alpha \ne 1$
\begin{align*}
c_\infty(k)  =&\frac{1}{8\alpha (\alpha-1)\Gamma^+(k-2\alpha,\xi)} \left( -\Gamma^+(k - 2 \alpha, \xi) - 2\frac{\alpha (\alpha - 1/2)^2 \xi^{2} \Gamma^+(k - 2 \alpha - 2, \xi)}{(\alpha - 1)} \right. \\ 
&\left.+ 8 \alpha (\alpha - 1/2) \xi \Gamma^+(k - 2 \alpha - 1,\xi) \right.\\ 
&\left.+ 4\xi^{4\alpha - 2} \Gamma^+(k - 6 \alpha + 2, 
      \xi) \left( \frac{2^{ - 4\alpha}(3 \alpha - 1)}{(\alpha - 1)} + (\alpha - 1/2) B^-(1/2; 1 + 2 \alpha, -2 + 2 \alpha) \right)  \right.\\ 
&\left.+ \xi^{k-2\alpha} \Gamma(2\alpha+1)e^{-\xi} U(2\alpha+1,1+k-2\alpha,\xi) \right. \\ 
&\left.- \xi^{4\alpha-2} \Gamma(2\alpha+1)\MeijerG{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}  \right)
\end{align*}

%\begin{align*}
%	c_\infty(k) 
%	&= \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma^+(k-6\alpha + 2,\xi_{\alpha,\nu})}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
%		\left(\frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha - 1)^2} + \frac{(\alpha - \frac{1}{2})B^-\left(\frac{1}{2},2\alpha + 1, 2\alpha - 2\right)}{2\alpha(\alpha - 1)}\right)\\
%	&\hspace{10pt}- \frac{\xi_{\alpha,\nu}^{4\alpha - 2}\Gamma(2\alpha + 1)}{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
%		\MeijerGnew{3}{0}{2}{3}{1,3-2\alpha}{3-4\alpha,-6\alpha+k+2,0}{\xi}\\
%	&\hspace{10pt}+ \frac{1}{8\alpha(\alpha - 1)}
%		\left(\frac{\xi_{\alpha,\nu}^{k-2\alpha}e^{-\xi}U(2\alpha+1,1+k-2\alpha,\xi_{\alpha,\nu})}
%		{\Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}-1\right)\\
%	&\hspace{10pt}- \frac{(\alpha - 1/2)^2 \xi_{\alpha,\nu}^2 \Gamma^+(k-2\alpha -2,\xi_{\alpha,\nu})}
%		{4(\alpha - 1)^2 \Gamma^+(k-2\alpha,\xi_{\alpha,\nu})}
%\end{align*}
while for $\alpha = 1$
\begin{align*}
	c_\infty(k) &= \frac{9 \eta^3}{2 k!} 	
		\Gamma^+(k-3,\eta)-\frac{\xi_{\alpha,\nu}^4}{k!}\frac{7+\pi^2}{4}\Gamma^+(k-4,\eta)\\
	&\hspace{10pt}+ \frac{\eta^k}{2k!}\int_0^1 (1-4z+3z^2)\ln(1-z)z^{1-k}e^{-\eta/z}\dd z\\ 
	&\hspace{10pt}+ \frac{\eta^k}{k!}\int_0^1 z^{3-k} \Li_2(z) e^{-\eta/z} \dd z,
\end{align*}
with $\eta = 4\nu/\pi$ and $\Li_2(z) = \sum_{t = 1}^\infty z^t/t^2$, the dilogarithm function.
\end{theorem}

From the exact expression for $c_\infty(k)$ we obtain its asymptotic behavior as $k \to \infty$. For this we first define, for any $\frac{1}{2} < \alpha < \frac{3}{4}$,
\begin{equation}\label{eq:def_C_alpha}
	C_\alpha = \frac{2^{-4\alpha - 1}(3\alpha - 1)}{\alpha(\alpha-1)^2} 
	+ \frac{\alpha - \frac{1}{2}}{2(\alpha - 1)\alpha} B^-(\frac{1}{2},2\alpha + 1, 2\alpha - 2)
	- \frac{1}{4(\alpha - 1)}B(2\alpha, 3\alpha - 4).
\end{equation}
Moreover, to simplify the statement we define the scaling function 
\begin{equation}\label{eq:def_scaling_function}
s_\alpha(k) = \begin{cases} 
		k^{4\alpha-2} &\frac{1}{2}<\alpha<\frac{3}{4}, \\
		\frac{k}{\log(k)} & \alpha = \frac{3}{4}, \\
		k &\alpha > \frac{3}{4}.
\end{cases}
\end{equation}
